---
title: "Myanmar Secondary Data Analysis - Outline"
author: "mz"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  word_document:
    fig_caption: yes
    fig_height: 4.5
    fig_width: 5
    reference_docx: StyleReference.docx
    toc: yes
bibliography: ../sources/myanmar-mz.bib
---
```{r setup, include = FALSE }
require(rgdal)
require(RColorBrewer)
require(classInt)
load(file = "../sources/data/clean/pop.map.RData")
source("../analysis/scripts/02-Functions.R")
```
_This is a draft outline of the secondary data analysis chapter for the Myanmar ageing farmers report._

_This is tentative, with placeholders for possible charts/maps, and indication of available variables and datasets._

# Demographic - social, economic; Households - structure, income, vulnerability

## 2014 Census 

The Myanmar Information Managment Unit is a well harmonized online resource for both cleaned up census data and GIS resources to match the administrative levels used in the 2014 census. [@MIMU2014]

### Population Based Dataset - Township level data

There are 330 townships - or rather there were that many in the 2014 census - for each of which almost 280 population aggregate variables are available. The list of variables is at the end of this document. 

Figure 1 is just a quick map of all the 330 townships, highlighting the two of special interest, and scatterplot of township level data, with the relevant areas highlighted. 

Any of these variables can be mapped, or plotted against eachother, like e.g. the ones in Figure 2. 


```{r fig_townships, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 1 left: Map of 330 Myanmar townships with Mandalay and Ayeyarwady towhnsips highlighted; right: township level ecological correlation between sex ratios and old age (65+) dependency ratios. "}
m <- cbind(c(1,1), c(2,2), c(2,2))
layout(m)
par(mar = c(0,0,0,0))
plot(ShpMMRTownship)
plot(ShpMMRTownship[ShpMMRTownship@data$ST %in% c("Mandalay") ,], col="orange", add=TRUE)
plot(ShpMMRTownship[ShpMMRTownship@data$ST %in% c("Ayeyarwady") ,], col="red", add=TRUE)
par(mar = c(5.1, 4.1, 4.1, 2.1))
plot(unlist(ShpMMRTownship@data[10+15]), unlist(ShpMMRTownship@data[31+15]), col = "gray", pch = 19,
     xlab = "Sex ratio", ylab = "Old age dependency ratio")
points(unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Mandalay") ,10+15]), 
       unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Mandalay") ,31+15]),
       col="orange", pch = 19)
points(unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Ayeyarwady") ,10+15]), 
       unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Ayeyarwady") ,31+15]),
       col="red", pch = 19)
legend("topright", col = c("red", "orange"), legend = c("Ayeyarwady", "Mandalay"), 
       bty = "n", pch =19)
```

<br> 

```{r fig_pop_map, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 2: Cloropleth maps of Myanmar at township level (330) - left Sex ratio of rural population, right old age dependency ratio (over 65) "}
par(mar = c(0,0,0,0))
par(mfrow = c(1,2))
# rural sex ratio
col <- FunMNTownMap(ShpMMRTownship@data$Rural.population...Sex.ratio,
             10,
             seq(0,200,20))
legend("topright", fill=attr(col, "palette")[4:9], 
       legend = names(attr(col, "table"))[4:9], bty="n",
       title = "Rural sex ratio")

# old age dependency ratio
col <- FunMNTownMap(ShpMMRTownship@data$Selected.age.groups.and.dependency.ratios...Old.dependency.ratio,
             5,
             seq(0,25,5), pal = brewer.pal(9, "Blues"))
legend("topright", fill=attr(col, "palette"), 
       legend = names(attr(col, "table")), bty="n",
       title = "Old age dependency ratio")
```


Of course all of these also be zoomed in to just the region of interest, and e.g. Figure 3 shows the cloropleth maps for literacy rates for all the townships in both the states of interest. 

```{r fig_zoom_in, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 3: Zoom into Mandalay townships on left (28) and Ayeyarwady townships on the right (26) on single variable - Literacy rate for both sexes"}
par(mfrow = c(1,2))
col <- FunMNTownMapS(var = 70, town = "Mandalay",
             n = 6,
             seq(88,100,2), pal = brewer.pal(9, "Reds"),
             mar = c(1,1,1,2))
legend("topleft", fill=attr(col, "palette"), 
       legend = names(attr(col, "table")), bty="n",
       title = "Literacy rate")

FunMNTownMapS(var = 70, town = "Ayeyarwady",
             n = 6,
              seq(88,100,2), pal = brewer.pal(9, "Reds"),
             mar = c(1,2,1,1))


```

All of these can of course be aggregated up to district and/or state and region levels and mapped or plotted accordingly. 

### Household Based Dataset - Township level data

All of this applies to the household level data as well. A list of the variables available is at the end of this document for reference. 

Of course a combination is also possible, as for example in Figure 4, which looks at the proportion of female headed households across the 330 townships, and also adds a zoomed map of both the Yangon region and Naypyitaw, and a histograms that let us compare the distribution within each of the regions with the distribution nationally.

```{r fig_testmap, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 4: Mean household size in 330 townships (left), in Mandalay top and Ayeyarwady bottom, along with histograpms showing the relative distirbutions of each region's townships compared to the national one. "}
m <- cbind(c(1,1), c(2,3), c(4,5))
layout(m)

col <- FunMNTownMap(unlist(ShpMMRTownship@data[309]),
             n = 8,
             seq(3,7,.5), pal =  brewer.pal(9, "YlGn") )
legend("bottomleft", fill=attr(col, "palette"), 
    legend = names(attr(col, "table")), bty="n",
     title = "% Female-headed HH")
rect(93.40 ,20.05,98.32, 23.82, border = "red")
rect(93.19 ,15.55, 97.07, 18.62, border = "red")
FunMNTownMapS(var = 309, town = "Mandalay",
             n = 8,
             seq(3,7,.5), pal =  brewer.pal(9, "YlGn"),
             mar = c(1,1,1,1))
npt <- par("usr")

FunMNTownMapS(var = 309, town = "Ayeyarwady",
             n = 8,
             seq(3,7,.5), pal =  brewer.pal(9, "YlGn"),
             mar = c(1,1,1,1))
yng <- par("usr")
par(mar = c(2,1,2,1))

FunMNTownHistS(309, town = "Mandalay",  main = "Mandalay Average HH size", col = "orange")
FunMNTownHistS(309, town = "Ayeyarwady",main = "Ayeyarwady Average HH size", col = "red")

```

### Occupation-Industry

Still using 2014 census data (BaselineData_Census_Occupation_Industry_MIMU_Jan2016) [@MIMU2014] the occupation/industry tables are summarised bellow. Populaiton pyramids, etc. Geography only goes to regional level though, so mapping is limited. 

Economic Activity (status):

* 15 Regions 
    + age groups - over 10  (14)
        - male/female


Economic Activity (status):       

* urban/rural (15)
    + age groups - over 10  (14)
    

Occupation (9 categories, incl. "skilled agricultural, forestry and fishery workers"):

* urban/rural (15)
    + age groups - over 10  (13)
    

Occupation (9 categories, incl. "skilled agricultural, forestry and fishery workers"):

* 15 Regions 
      + male/female

    
    
Industry (16 categories, incl. " Agriculture, forestry and fishing"):

* urban/rural (15)
    + age groups - over 10  (13)
    

Industry (16 categories, incl. " Agriculture, forestry and fishing"):

* 15 Regions 
      + male/female

    
    
_e.g. we can do populaiton pyramids with eomployment struture etc with this stuff._



## World Population Prospects

_For population growth, age composition, dependency ratios etc. estimated 1950-2015, and projected until 2050 as well as urbanisation etc. there is the UN data [@UNPD2015]..._


# Agricultural - food security, crops, land 

## International Rice Research Institute

International Rice Research Institute data on trends etc. [@IRRI2016] has statistics on production, yield etc. which can be plotted as trend line charts. List of variables in Appendix

So for example here is rice yeild, export ( acdcording to the USDA and dotted also according to the FAO) and per capita consumption of rice over the whole period:

```{r fig_irri, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=5,fig.keep='high', fig.cap="Figure 5: Some IRRI trends: Rice paddy yield (top), export quantitiy (middle) and per capita rice consumption (bottom).  "}
irri.data <- read.csv("../sources/data/clean/irri.data.csv")

par(mfrow=c(3,1))
par(mar = c(3,4,1,1))
plot(irri.data$Year[irri.data$Variable == "YIELD - PADDY"  ], 
     irri.data$Value[irri.data$Variable == "YIELD - PADDY"  ], 
     type = "l", xlim = c(1960, 2015), bty = "n", xlab = "",
     ylab = "Yield", lwd = 2)
plot(irri.data$Year[irri.data$Variable == "EXPORT QUANTITY"  &
                      irri.data$Source == "USDA"], 
     irri.data$Value[irri.data$Variable == "EXPORT QUANTITY" &
                       irri.data$Source == "USDA" ] , 
     type = "l", xlim = c(1960, 2015),
     bty = "n", xlab = "",
     ylab = "Export quantity", lwd = 2)
lines(irri.data$Year[irri.data$Variable == "EXPORT QUANTITY"  &
                      irri.data$Source == "FAO"], 
     irri.data$Value[irri.data$Variable == "EXPORT QUANTITY" &
                       irri.data$Source == "FAO" ] , 
     type = "l", xlim = c(1960, 2015), lty = 3, lwd = 2)
plot(irri.data$Year[irri.data$Variable == "RICE CONSUMPTION PER CAPITA"  ], 
     irri.data$Value[irri.data$Variable == "RICE CONSUMPTION PER CAPITA"  ], 
     type = "l", xlim = c(1960, 2015), bty = "n", xlab = "",
     ylab = "Per capita consumption", lwd = 2)




```

# Appendix 1: Variables

Census population level variable list: 

```{r, echo = FALSE}
load("../sources/data/clean/census.pop.varz.RData")
varz
```
<br>

Census household level variable list: 

```{r, echo = FALSE}
load("../sources/data/clean/census.hh.varz.RData")
varz
```
<br>

IRRI variable list

```{r, echo = FALSE}
unique(irri.data$Variable)
```

##### References

<br>