---
title: "Myanmar Secondary Data Analysis - Draft Chapter"
author: mz
bibliography: ../sources/myanmar-mz.bib
output: 
 word_document:
  reference_docx: StyleReference.docx
  fig_width: 5
  fig_height: 4.5
  fig_caption: true
 
---
```{r setup, include = FALSE }
require(rgdal)
require(RColorBrewer)
require(classInt)
load(file = "../sources/data/clean/pop.map.RData")
source("../analysis/scripts/02-Functions.R")
```
_This is a draft outline of the secondary data analysis chapter for the Myanmar ageing farmers report. Tentative headings are based on SH email 11.8.16._


_This is tentative, with placeholders for possible charts/maps, and indication of available variables and datasets._

# Demographic - social, economic

## 2014 Census 

The Myanmar Information Managment Unit is a well harmonized online resource for both cleaned up census data and GIS resources to match the administrative levels used in the 2014 census. [@MIMU2014]

### Population Based Dataset - Township level data

There are 330 townships - or rather there were that many in the 2014 census - for each of which almost 280 population aggregate variables are available. The list of variables is at the end of this document. 

Figure 1 is just a quick map of all the 330 townships, highlighting the two of special interest, and scatterplot of township level data, with the relevant areas highlighted. 

Any of these variables can be mapped, or plotted against eachother, like e.g. the ones in Figure 2. 


```{r fig_townships, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 1 left: Map of 330 Myanmar townships with Yangon and Nay Pyi Taw towhnsips highlighted; right: township level ecological correlation between sex ratios and old age (65+) dependency ratios. "}
m <- cbind(c(1,1), c(2,2), c(2,2))
layout(m)
par(mar = c(0,0,0,0))
plot(ShpMMRTownship)
plot(ShpMMRTownship[ShpMMRTownship@data$ST %in% c("Yangon") ,], col="orange", add=TRUE)
plot(ShpMMRTownship[ShpMMRTownship@data$ST %in% c("Naypyitaw  Council") ,], col="red", add=TRUE)
par(mar = c(5.1, 4.1, 4.1, 2.1))
plot(unlist(ShpMMRTownship@data[10+15]), unlist(ShpMMRTownship@data[31+15]),
     xlab = "Sex ratio", ylab = "Old age dependency ratio")
points(unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Yangon") ,10+15]), 
       unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Yangon") ,31+15]),
       col="orange", pch = 19)
points(unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Naypyitaw  Council") ,10+15]), 
       unlist(ShpMMRTownship@data[ShpMMRTownship@data$ST %in% c("Naypyitaw  Council") ,31+15]),
       col="red", pch = 19)
legend("topright", col = c("red", "orange"), legend = c("Yangon", "Natpyitaw"), 
       bty = "n", pch =19)
```

<br> 

```{r fig_testmap, include = TRUE, echo = FALSE, results="hide", warning = FALSE, fig.width=8, figh.height=8,fig.keep='high', fig.cap="Figure 2: Test Map of Myanmar - left: township level, right: region/state level"}
par(mar = c(0,0,0,0))
par(mfrow = c(1,2))
# rural sex ratio
col <- FunMNTownMap(ShpMMRTownship@data$Rural.population...Sex.ratio,
             10,
             seq(0,200,20))
legend("topright", fill=attr(col, "palette")[4:9], 
       legend = names(attr(col, "table"))[4:9], bty="n",
       title = "Rural sex ratio")

# old age dependency ratio
col <- FunMNTownMap(ShpMMRTownship@data$Selected.age.groups.and.dependency.ratios...Old.dependency.ratio,
             5,
             seq(0,25,5), pal = brewer.pal(9, "Blues"))
legend("topright", fill=attr(col, "palette"), 
       legend = names(attr(col, "table")), bty="n",
       title = "Old age dependency ratio")


```


Of course all of these also be zoomed in to just the region of interest, and e.g. 


### Household Based Dataset


# Agricultural - food security, crops, land 
#  Households - structure, income, vulnerability

# Variables:

Census population level variable list: 

```{r}
load("../sources/data/clean/census.pop.varz.RData")
varz
```
<br>

##### References

<br>